Feature selection in fault classification of rotating machinery

### 2024-03-17 iit-src/paper.tex
Start creating figures for iit-src article
PCA analysis and load whole feature set

Figures:

Signal analysis
- 1ks obr. Mafaulda ABVT simulator
- 1ks plot (histogram of td signal)?
- 1ks plot (6x subplots) Mafaulda welch from each fault (1s, 2**14 window, hann window)  - largest severity - 2500 rpm
- 1ks plot (6x subplots) Custom dataset - each place in one day spectrum (5s segment)

Feature analysis:
Mafaulda (3) a Custom (4) 
- 1 ks table (how many faults have how many recordings)
- 1 ks plot (2 lines TD, FD) - numer of PC vs. explained variance
- 1 ks plot (2x subplots TD, FD) - loading plot (PC2)
- 1 ks (4 subplots) custom: all machines, pumps, compressors, motors

>>>>

Figures:
- 1ks obr. Mafaulda ABVT simulator
- 1ks obr. (2ks subplots) machine and compressor measurement places with red squares
- 1 ks obr. device

Signal analysis

- 1ks plot (histogram of td signal)?
- 1ks plot (6x subplots) Mafaulda welch from each fault (1s, 2**14 window, hann window)  - largest severity - 2500 rpm
- 1ks plot (6x subplots) Custom dataset - each place in one day spectrum (5s segment)

Feature analysis:
Mafaulda (4) a Custom (4) 
- 1 ks table (how many faults have how many recordings)
- 1 ks plot (2 lines TD, FD) - numer of PC vs. explained variance
- 1 ks plot (2x subplots TD, FD) - loading plot (PC2)

% TODO
- 1 ks (5 subplots) scatter: mafaulda, all machines, pumps, compressors, motors
